### 2019-06-08 2-Chapters/3-Chapter/chapter3.tex
Proofread all Ch2 and added x := rhs when needed

\TODOL{C'est bizarre ce problème d'espacement vertical ici... je ne sais pas comment le corriger !}

@@

We start by explaining how SMPyBandits simulates MAB problems, by detailing its components:
MAB problems (single- or multi-players),
and reward distributions.
%
We then detail how it implements MAB algorithms (\eg, \UCB),
and what kind of information is displayed, saved and plotted after a batch of simulations of bandit problems.

The main goal of the library is to be easily able to simulate MAB algorithms (\eg, three algorithms like \UCB, \klUCB{} and Thompson sampling) on one or more bandit models (single- or multi-player) defined by the number of arms $K$ and the distributions $\nu_k$, for some time from $t=1$ to the horizon $T$.
After the simulation, the library then displays statistical summary of the (mean) rewards accumulated by each algorithm, as well as regret and other visualizations.
The same problem is simulated for $N$ independent repetitions (\eg, $N=100$) in order to show mean results with a low variance.

@@

\paragraph{Simulation loop.}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithm, and a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem and one or more algorithms,
    % \item
    Then, for $t=1$ to $t=T$ (known before hand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm,
    % \item
    At the end, compute the cumulated reward, the regret, plot visualizations etc.
% \end{itemize}
%
Note that the second step is repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(Y_{k,t})_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms.

\paragraph{Simulation loop for multi-player bandit.}

@@

For more details, an interested reader can refer to the following Jupyter notebook \cite{jupyter}:
\begin{small}
    \href{https://smpybandits.github.io/notebooks/Easily_creating_MAB_problems.html}{\texttt{SMPyBandits.GitHub.io/notebooks/Easily\_creating\_MAB\_problems.html}}
\end{small}

We have not yet tried to add support for higher dimensional distributions of rewards, \eg, linear bandit, but it would be an interesting extension of SMPyBandits.
%
However, note that our library does support finite-state real-valued Markov MAB models, where arms do not correspond to distributions but to Markov chains, in the two variants of \emph{rested} or \emph{restless} Markov chains, as introduced by \cite{Anantharam87b}.

\subsection{MAB algorithms}

@@

Launching simulations is easy, for instance this snippet shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, an horizon of $T=10000$ and on $4$ CPUs.
It takes about $20$ minutes, on a standard $4$-cores $64$ bits GNU/Linux laptop.
Using environment variables (\texttt{N=1000} etc) in the command line is not required, but it is convenient:

>>>>

% \TODOL{C'est bizarre ce problème d'espacement vertical ici... je ne sais pas comment le corriger !}

@@

We start by explaining how SMPyBandits simulates MAB problems, by detailing its components:
MAB problems (single- or multi-players),
and reward distributions.
%
We then detail how it implements MAB algorithms (\eg, \UCB),
and what kind of information is displayed, saved and plotted after a batch of simulations of bandit problems.
%
%
The main goal of the library is to be easily able to simulate MAB algorithms (\eg, three algorithms like \UCB, \klUCB{} and Thompson sampling) on one or more bandit models (single- or multi-player) defined by the number of arms $K$ and the distributions $\nu_k$, for some time from $t=1$ to the horizon $T$.
After the simulation, the library then displays statistical summary of the (mean) rewards accumulated by each algorithm, as well as regret and other visualizations.
The same problem is simulated for $N$ independent repetitions (\eg, $N=100$) in order to show mean results with a low variance.

@@

\textbf{Simulation loop.}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithm, and a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem and one or more algorithms,
    % \item
    Then, for $t=1$ to $t=T$ (known before hand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm,
    % \item
    At the end, compute the cumulated reward, the regret, plot visualizations etc.
% \end{itemize}
%
Note that the second step is repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(Y_{k,t})_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms.

\textbf{Simulation loop for multi-player bandit.}

@@

For more details, an interested reader can refer to the following Jupyter notebook \cite{jupyter}:
\href{https://smpybandits.github.io/notebooks/Easily_creating_MAB_problems.html}{\texttt{SMPyBandits.GitHub.io/notebooks/Easily\_creating\_MAB\_problems.html}}.\\
%
We have not yet tried to add support for higher dimensional distributions of rewards, \eg, linear bandit, but it would be an interesting extension of SMPyBandits.
%
However, note that our library does support finite-state real-valued Markov MAB models, where arms do not correspond to distributions but to Markov chains, in the two variants of \emph{rested} or \emph{restless} Markov chains, as introduced by \cite{Anantharam87b}.

\subsection{Multi-Armed Bandits algorithms}

@@

Simulations are easily executed, \eg, this snippet shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, an horizon of $T=10000$ and on $4$ CPUs.
It takes about $20$ min, on a $4$-core $64$-bit GNU/Linux laptop.
Environment variables (\texttt{N=1000} etc) in the command line are not required, but they are convenient.
